Supporting information

### 2019-09-03 EAshiklomanovSA2.Rmd
Fix SA2 formatting

@@

```{r pairwise_correlation_table, echo = FALSE, results = "asis"}
rma_display <- readRDS(file.path(npdir, "extdata", "rma-display.rds"))
kable(
  rma_display,
  "latex",
  booktabs = TRUE, longtable = TRUE,
  caption = paste("Pairwise reduced major axis (RMA) slope values",
                  "(Mean and 95pct credible interval)",
                  "for each plant functional type.",
                  "Values with asterisks indicate slopes",
                  "with credible intervals that don't intersect zero.")
)

@@

par(mfrow = c(2, 2))
for (i in 1:4) {
  plot(
    0, 0,
    type = "n",
    xlim = range(c(boot_lo[, i], boot_hi[, i]), na.rm = TRUE),
    ylim = range(ymiss_true[, i], na.rm = TRUE),
    xlab = "Estimate",
    ylab = "True value",
    main = colnames(iris)[i]
  )
  arrows(boot_lo[, i], ymiss_true[, i], boot_hi[, i],
         length = 0.01, col = "gray70", code = 3)
  points(boot_means[, i], ymiss_true[, i],
         pch = 19, col = grp_m)
  abline(0, 1, lty = "dashed")
  legend("bottomright", levels(grp_m),
         pch = 19, col = 1:3)
}
```

>>>>

(Page intentionally left blank)

```{r mean-compare-all, echo = FALSE, fig.cap = mca_cap, fig.position = "H"}
mca_cap <- paste(
  "Mean and 95% credible intervals on estimates of trait means for each plant functional type",
  "from the univariate, multivariate, and hierarchical models.",
  "For leaf lifespan and SLA, results were similar for mass- and area-based models,",
  "so only results from the mass-based model area shown.",
  "For some PFT-trait combination, where error bars are large due to the relatively",
  "uniformative prior, $y$ axes are constrained to facilitate comparison."
)
knitr::include_graphics(file.path(npdir, "figures", "manuscript", "mean_comparison_all.pdf"))
```

@@

```{r pairwise_correlation_table, echo = FALSE, results = "asis"}
rma_display <- readRDS(file.path(npdir, "extdata", "rma-display.rds"))
kable(
  rma_display,
  "latex",
  booktabs = TRUE, longtable = TRUE,
  caption = paste("Pairwise reduced major axis (RMA) slope values",
                  "(Mean and 95pct credible interval)",
                  "for each plant functional type.",
                  "Values with asterisks indicate slopes",
                  "with credible intervals that don't intersect zero.")
) %>%
  kableExtra::kable_styling(latex_options = "hold_position")

@@

# TODO: Fix these figure margins
par(mfrow = c(2, 2))
for (i in 1:4) {
  plot(
    0, 0,
    type = "n",
    xlim = range(c(boot_lo[, i], boot_hi[, i]), na.rm = TRUE),
    ylim = range(ymiss_true[, i], na.rm = TRUE),
    xlab = "Estimate",
    ylab = "True value",
    main = colnames(iris)[i]
  )
  arrows(boot_lo[, i], ymiss_true[, i], boot_hi[, i],
         length = 0.01, col = "gray70", code = 3)
  points(boot_means[, i], ymiss_true[, i],
         pch = 19, col = grp_m)
  abline(0, 1, lty = "dashed")
  legend("bottomright", levels(grp_m),
         pch = 19, col = 1:3)
}
```
